Computing Entropies With Nested Sampling

### 2017-06-26 paper/ms.tex
Paragraph about conditional entropy

>>>>

As the algorithm lets us calculate the entropy of any distribution which can
be sampled by MCMC, there are several options. The mutual information
can be written in the following three ways
\begin{align}
I(x; y) &= H(x) + H(y) - H(x, y) \\
I(x; y) &= H(y) - H(y|x) \\
I(x; y) &= H(x) - H(x|y).
\end{align}
In a Bayesian problem where $x$ is an unknown parameter and $y$ is data, the
first and second formulas would be very costly to compute, because of the
high dimensional probability distribution for the dataset.
